Dynamic Transition Analysis with TIMES

### 2018-08-02 doc/2019-01-poster/poster.tex

\setbeamercolor{block title}{fg=dblue!80,bg=white} % Colors of the block titles
\setbeamercolor{block body}{fg=black,bg=white} % Colors of the body of blocks
\setbeamercolor{block alerted title}{fg=white,bg=dblue!70} % Colors of the highlighted block titles
\setbeamercolor{block alerted body}{fg=black,bg=dblue!10} % Colors of the body of highlighted blocks
% Many more colors are available for use in beamerthemeconfposter.sty

@@

\usepackage{graphicx}  % Required for including images

@@

@@

@@

\author{
       % \textbf{ENERGY ANALYSIS DIVISION}\\
       % \textbf{I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions}\\
        Anshuman Chaube, James Stubbins, \textbf{Kathryn Huff}}
\institute{University of Illinios at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, IL 61801}
%----------------------------------------------------------------------------------------

@@

\begin{block}{Introduction}
Previous work has compared the impact of innovative energy technologies in 
various world regions using \textbf{static} scenario analyses 
\cite{chyong_chi_dynamics_2009,feng_system_2013,kikuchi_simulation-based_2017,li_energy_2010,pambudi_impact_2017,pambudi_future_2016}.  
We will simulate \textbf{dynamic} transition scenarios 
\cite{jebaraj_review_2006,pfenninger_energy_2014} aimed at minimizing carbon 
emissions in Japan by 2050. These scenarios will include realistic constraints 
regarding technology readiness (in terms of generation, transmission \& 
storage) and will combine multiple technologies in a single heterogeneous 
system model.
\end{block}

@@

%----------------------------------------------------------------------------------------
\begin{block}{Methodology}
        \textbf{The Integrated MARKAL-EFOM System (TIMES)} model generator 
        \cite{loulou_documentation_2005} 
        \cite{seebregts_energy/environmental_2002} optimizes energy systems 
        using linear and mixed-linear algorithms. A user-defined objective 
        function (such as minimizing carbon emissions or costs) is solved within user defined constraints such as energy generation demand.

\begin{description}
        \item[\textbf{Sector Analysis:}] TIMES models can resolve generation and 
                 consumption by sector (commercial, industrial, residential, 
                 building etc). 
         \item[\textbf{Regional Analysis:}] TIMES can also resolve regions.
         \item[\textbf{Post-Processing:}] Many metrics are automatically postprocessed 
                 (i.e. energy intensity, thermal energy efficiency, 
                 transmission capacity). 
         \item[\textbf{Constrained Optimization}] Modeling technology deployment 
                 transition as a constrained optimization problem will
                 drive insights.
 \end{description}

         The key objective function is minimization of carbon emissions in 2050 
         and a key
         constraint will be that deployed generation capacity must meet energy 
         demand. This can na\"ively be written:

\begin{align}
        \intertext{minimize:}
        &\sum_g^G C_g x_g 
        \intertext{subject to:}
        &\sum_g^Gx_g = d
        \intertext{where}
        C_g =& \mbox{ carbon emissions from generation component g}\\
        x_g =& \mbox{ deployment of generation component g}\\
        d =& \mbox{ generation demand}
\end{align}

A simple \textbf{static} formulation is straightforward to write, as above.  
However this  formulation is quickly complicated by including \textbf{dynamic 
time} as well as additional constraints (energy storage, variable demand, 
$CO_2$ sequestration, efficiency, costs, etc.)
\end{block}

\end{column} % End of column 2, top half
\end{columns}
%=======================================================
% Double Wide Figure Column 
%=========================================================
\input{model-fig}

@@

%----------------------------------------------------------------------------------------
%	TAKE AWAY
%----------------------------------------------------------------------------------------

        \begin{alertblock}{Take Aways}
	\begin{itemize}
                \item Dynamic simulation of Japan's energy system transition in 
                        the TIMES model generator will help develop near-term 
                        decarbonization strategies.
                \item Policymakers will benefit from identification of high 
                        impact technologies, and creation of R\&D investment 
                        and infrastructure development timelines.  
                \item Simulations will quantify system sensitivity to 
                        technology readiness. 
                \item Dynamic analysis will identify potential transition 
                        bottlenecks.
	\end{itemize}
        \end{alertblock}

%--------------------------------------------------------
% PROJECT TIMELINE
%---------------------------------------------------------
\begin{block}{Timeline}
        \input{timeline}
\end{block}

\begin{block}{References}
        {\small\bibliographystyle{abbrv} 
        \bibliography{poster}}
\end{block}

>>>>

\setbeamercolor{block title}{fg=dblue!80,bg=white} % Colors of the block titles
\setbeamercolor{block body}{fg=black,bg=white} % Colors of the body of blocks
\setbeamercolor{block alerted title}{fg=white,bg=dblue!70} % Colors of the highlighted block titles
\setbeamercolor{block alerted body}{fg=black,bg=dblue!10} % Colors of the body of highlighted blocks
\setbeamertemplate{caption}[numbered]

% Many more colors are available for use in beamerthemeconfposter.sty

@@

\usepackage{graphicx}  % Required for including images
\usepackage{hyperref}
\usepackage{cite}

@@

\usepackage{amssymb}
\usepackage{pifont}
\usepackage{xcolor}
\newcommand{\greencheck}{{\color{green}\checkmark}}
\newcommand{\xmark}{{\color{red}\ding{55}}}

@@

\makeatletter
\def\beamer@andinst{\\[0em]}
\makeatother

@@

\author{
       % \textbf{ENERGY ANALYSIS DIVISION}\\
       % \textbf{I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions}\\
        Anshuman Chaube\inst{1}, Andrew Chapman\inst{2}, James Stubbins\inst{1}, \textbf{Kathryn Huff}\inst{1}}
\institute[shortinst]{ \inst{1} University of Illinois at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, USA \and \inst{2} International Institute for Carbon Neutral Energy Research (I$^2$CNER), Kyushu University, Fukuoka, Japan}
%----------------------------------------------------------------------------------------

@@

\begin{block}{Introduction}
Previous work has compared the impact of innovative energy technologies in 
various world regions using \textbf{static} scenario analyses 
\cite{kikuchi_simulation-based_2017,pambudi_impact_2017}.  
We are simulating \textbf{dynamic} transition scenarios 
\cite{pfenninger_energy_2014} aimed at optimizing energy supply to minimize carbon 
emissions in Japan to 80\% of 1990 levels by 2050, and maintaining these levels from 2050-2100. \\

Our model includes conventional energy sources such as \textbf{fossil fuels, nuclear, wind, solar, hydropower, and geothermal}, and applicable I$^2$CNER technologies like \textbf{post-combustion absorption-type carbon capture and sequestration, hydrogen production (steam reforming and photocatalytic conversion)}. \hfill \break

%\vspace{77mm}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{conv_nuc_elc}
\caption{\textbf{Scenario 1} (conventional, with new nuclear) Electricity Generation.}
\label{s1e}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{conv_nuc_co2}
\caption{\textbf{Scenario 1} (conventional, with new nuclear) CO$_2$ emissions.}
\label{s1c}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{conv_nonuc_elc}
\caption{\textbf{Scenario 2} (conventional, no new nuclear) Electricity Generation.}
\label{s2e}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{conv_nonuc_co2}
\caption{\textbf{Scenario 2} (conventional, no new nuclear) CO$_2$ emissions.}
\label{s2c}
\end{figure}

@@

%----------------------------------------------------------------------------------------
\begin{block}{Methodology}
        \textbf{The Integrated MARKAL-EFOM System (TIMES)} model generator 
        \cite{loulou_documentation_2005} 
        \cite{seebregts_energy/environmental_2002} optimizes energy systems 
        using linear and mixed-linear algorithms. A user-defined objective 
        function is solved within user defined constraints.\\
\textbf{Key assumptions:}

\begin{itemize}
        \item\textbf{Objective function:} System cost.

         \item\textbf{Constraints:} CO$_2$ emissions, demand (+1.7\% per year) \cite{noauthor_electricity_2017}.

         \item Hydropower and geothermal capacity held constant \cite{noauthor_energy_2018}.

         \item Variation in costs of wind, solar, and photocatalytic H$_2$ production is given in Fig. \ref{cost}.

         \item All new nuclear reactors are ABWRs \cite{rothwell_real_2006}.

         \item Growth rate and maximum annual increase in capacity of nuclear, wind and solar is based on data and trends seen in USA, China, and Japan. \cite{noauthor_electricity_2017,noauthor_energy_2018,eia_international_nodate,eia_monthly_2018,iea-pvps_snapshot_2018}

         \item \textbf{Carbon capture and sequestration and steam reforming:} Deployed in 2030, with its costs reducing by 2050 as per projected trends. \cite{kato_energy_2016}

         \item \textbf{Hydrogen production:} Steam reforming deployed in 2030. Photocatalytic hydrogen production deployed in 2050, assumed to be cost-competitive with other H$_2$ production technologies. \cite{kato_energy_2016} \cite{acar_comparative_2014} \\

 \end{itemize}

We have modeled \textbf{four scenarios} with different energy technologies enabled: \hfill \break

\begin{tabular}{c c c c c}

\textbf{Scenario} & \textbf{Figures}         & \textbf{Conventional}      & \textbf{I$^2$CNER}   & \textbf{New nuclear} \\
                  &                          & \textbf{technology}        &  \textbf{technology} & \textbf{reactors}    \\
1                 & Fig. \ref{s1e}\&\ref{s1c}&      \greencheck           &         \xmark       &      \greencheck     \\ 
2                 & Fig. \ref{s2e}\&\ref{s2c}&      \greencheck           &         \xmark       &         \xmark       \\ 
3                 & Fig. \ref{s3e}\&\ref{s3c}&      \greencheck           &      \greencheck     &      \greencheck     \\ 
4                 & Fig. \ref{s4e}\&\ref{s4c}&      \greencheck           &      \greencheck     &         \xmark       \\
\end{tabular}

%\vspace{65 mm}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{legend}
%\caption{Legend}
\label{legend}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{i2cner_nuc_elc}
\caption{\textbf{Scenario 3} (with I$^2$CNER tech and new nuclear) Electricity Generation.}
\label{s3e}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{i2cner_nuc_co2}
\caption{\textbf{Scenario 3} (with I$^2$CNER tech and new nuclear) CO$_2$ emissions.}
\label{s3c}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{i2cner_nonuc_elc}
\caption{\textbf{Scenario 4} (with I$^2$CNER tech, no new nuclear) Electricity Generation.}
\label{s4e}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{i2cner_nonuc_co2}
\caption{\textbf{Scenario 4} (with I$^2$CNER tech, no new nuclear) CO$_2$ emissions.}
\label{s4c}
\end{figure}

\end{column} % End of column 2, top half
\end{columns}
%=======================================================
% Double Wide Figure Column 
%=========================================================
%\input{model-fig}

@@

%----------------------------------------------------------------------------------------
%	TAKE AWAY
%----------------------------------------------------------------------------------------
\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{cost}
\caption{Cost variation in solar, wind, and photocatalytic H$_2$ production.}
\label{cost}
\end{figure}
         \begin{alertblock}{Take Aways}
	\begin{itemize}
                \item Nuclear power has the lowest emissions intensity and it results in the most economical energy supply.

                \item Without nuclear and I$^2$CNER technology, solar and offshore wind must be deployed in a 1:2 ratio for grid resilience.

                \item Photocatalytic H$_2$ and offshore wind can meet I$^2$CNER targets in the absence of nuclear, but at significantly higher cost.

                \item Technologies with the highest impact so far: nuclear power, offshore wind, photocatalytic H$_2$ generation, solar power
	\end{itemize}
        \end{alertblock}

%--------------------------------------------------------
% PROJECT TIMELINE
%---------------------------------------------------------
\begin{block}{Limitations and Future work}
    \begin{itemize}

    \item Model focuses entirely on \textbf{electricity supply sector}.

    \item The cost of fossil fuels, geothermal, hydropower, steam reforming and nuclear is held constant.

    \item No limit on penetration of solar or wind except maximum potential.

    \item Annual timesteps and annually averaged capacity factors limit ability to capture seasonal and daily variation in wind and solar.

    \item Capture realistic, gradual transition behaviour and fluctuations in demand due to population decline in Japan.

    \item Incorporation of more I$^2$CNER technologies.

    \item Sensitivity analysis to maximize impact of I$^2$CNER technology.

    \item Detailed cost analysis

    \item Incorporation of natural gas and/or energy storage technologies to supplement renewable energy and I$^2$CNER technology.

    \end{itemize}
\end{block}

\begin{block}{References}
        {\footnotesize\bibliographystyle{ieeetr} 
        \bibliography{2019-chaube-i2cner-poster}}
\end{block}
